\subsection{Constant-Round Zero Knowledge}
Simply runs $n\cdot\abs{E}$ iteration in parallel is not working. The simulator will need to guess all $N\stackrel{def}{=} n\cdot\abs{E}$ edges correctly to success. The probability of guessing correctly is $\abs{E}^{-n\cdot\abs{E}}$, which is exponentially small. Note that rewinding doesn's solve this problem. The adversaries can simply choose a new randomness each time. In fact, Goldreich and Krawczyk showed that this paralle protocol is not {\it black-box zero-knowledge}, and no constant-round public-coin proof for a language not in ${\sf BPP}$ is boack-box zero-knowledge. Althougth there are no known constructions of adversaries, the lack of known attack is not sufficient to conclude that a protocol is secure. Thus, an alternative protocol is needed.

The solution presented by Goldreich and Kahan is to simply have the verifier commit to its query before the prover sends its commitments. This prevents a malicious verifier from changing its query during rewinding. Details appear in Protocol~\ref{proto:zk-3-color-constant}. \\ \\
\begin{adjustbox}{minipage=1\linewidth,fbox}
\begin{protocol}[The Goldreich-Kahan Proof System]$ $
    \begin{description}
        \item[Common input.] a graph $G=(V,E)$ with $V=\{v_1,\ldots,v_n\}$
        \item[Auxiliary input for $P$.] a coloring of the graph $\psi:V\to\{1,2,3\}$ such that \\ 
        for every $(v_i,v_j)\in E$ it holds that $\psi(v_i)\neq\psi(v_j)$
        \item[Primitives] Let $\com$ be an non-interactive perfectly-binding commitment scheme,\\ $\com_h$ be a two-round perfectly-hiding commitment scheme. 
        \item[The proof system:] Repeating the following $n\cdot\abs{E}$ times:
        $ $\newline\newline
        \begin{adjustbox}{minipage=0.6\linewidth}
            \begin{tabular}{lcl}
            $P(G,\psi;r_P)$ & & $V(G;r_V)$ \\
            \\
            Send the first message, denoted 
            \\by $\alpha$ of $\com_h$ & \rextlinearrow{\alpha}{15} & \\
            & & choose $N\stackrel{def}{=}n\cdot\abs{E}$ random \\
            & & edges $q=(e_1,\ldots,e_N)$, \\
            & & where $e_i\in E$ \\
            &\lextlinearrow{c}{15}& $c=\com_h(q)$\\
            Continue as basic protocol~\ref{proto:zk-3-color-nonconstant}&&\\
            & \rextlinearrow{\com(\phi(v))}{15} & \\
            & \lextlinearrow{\decom(c)}{15}& send decommitmet of $c$\\
            {\bf If} the decommitment is invalid \\
            {\bf abort}& &\\
            {\bf Otherwise} send the decommitment \\
            of edges & \rextlinearrow{\decom(v)}{15}& If all checks pass outputs 1\\
            \end{tabular}
        \end{adjustbox}
        \\
    \end{description}\label{proto:zk-3-color-constant}
\end{protocol}
\end{adjustbox}
\\ \\
First thought of a possible simulator is:
\begin{enumerate}
\item $\simu$ sends $alpha$ to $V^*$
\item $\simu$ receives commitment $c$ from $V^*$
\item $\simu$ sends $V^*$ garbage commitments and receives its decommitment. If the decommitment is not valid, it aborts. Otherwise, denote the decommitted string by 
$q=(e_1,\ldots,e_N)$.
\item $\simu$ rewinds $V^*$, send a new $\com(\phi(v))$ that suit $q$. Repeat this step until $V^*$ send a valid decommitment
\item $\simu$ sends $V^*$ the decommitment to the nodes on the committed edge and outputs whatever $V^*$ outputs.
\end{enumerate}
There are two issues in this simple simulator. First, since the commitment to $q$ is perfectly hiding and thus only {\it computationally-binding}. It is possible that the $V^*$ decommits to a valid $q'\neq q$. Second, we are not able to show that the simulator is running in expected polynomial-time. Let $\epsilon$ denote the probability that $V^*$ does not abort. At first glance, one may conclude that the expected running time of the simulator is $(1-\epsilon)+\epsilon\cdot\frac{1}{\epsilon}$. However this is only in the case that commitment is modeled as ``perfect envelopes''. The true running is:
$$poly(n)\cdot(1-\epsilon(n)+\epsilon(n)\cdot\frac{1}{\epsilon(n)-\mu(n)}),$$
which might be exponential in $n$.
\begin{theorem} Let $\com_h$ and $\com$ be {\it perfectly-hiding} and {\it perfectly-binding} commitment schemes, respectively, with security in the presence of non-uniform PPT adversaries. Then Protocol~\ref{proto:zk-3-color-constant} is black-box computational zero knowledge with an expected polynomial-time simulator.
\end{theorem}
\begin{proof}
The simulator is stated as Algorithm~\ref{alg:zk-3-color-constant-sim}. We have three claims to complete our proof.
\begin{claim} Algorithm~\ref{alg:zk-3-color-constant-sim} runs in expected polynomial time in $n$.
By Chernoff bound, we have $\widetilde{\epsilon}$ is not within a constant factor of $\epsilon(n)$ is at most $2^{-n}$.
Consider two cases:
\begin{enumerate}
\item $\widetilde{\epsilon}$ is not within a constant factor of $\epsilon(n)$.
	The running-time is bounded by $2^{n}$ and this happens with probability $2^{-n}$. This add a total $poly(n)$ to expected running-time.
\item $\widetilde{\epsilon}/\epsilon=O(1)$.
We can bound the expected running-time of $\simu$ by
$$poly(n)\cdot\epsilon(n)\cdot(\frac{12n}{\epsilon(n)}+n\cdot\frac{n}{\widetilde{\epsilon}})=poly(n)$$
\end{enumerate}
\end{claim}
\begin{claim} The probability that Algorithm~\ref{alg:zk-3-color-constant-sim} outputs {\sf fails} is negligible.
Notice that:
$$\Pr[\simu \text{outputs \sf fails}]=\Pr[\text{does not obtain vaild decommitment in the loop}]+\Pr[\text{runs for }2^n\text{steps}]$$
We already saw that $\simu$ runs in expected poly-time, therefore the probability that it runs for $2^n$ steps is negligible.
Now consider the case the $\simu$ does not obtain valid in all $n\cdot\frac{n}{\widetilde{\epsilon}}$ attemps. Recall that $\epsilon(n)$ denotes the probability that $V^*$ decommits when given commitments to all zeros. Next there exists an negligible function $\mu(\cdot)$ such that $V^*$ decommits when given commitments in line 20 of Algorithm~\ref{alg:zk-3-color-constant-sim}. $\mu(n)$ needs to be negligible or $V^*$ can be used to break {\it computationally-hiding} of $Com_h$. Now consider following cases:
\begin{enumerate}
\item $\epsilon(n)\leq 2\mu(n)$: This means $V^*$ decommits its query string with negligible probability. The probability of $\simu$ reaches the rewinding phase is negligible.
\item $\epsilon(n)> 2\mu(n)$: We have $\frac{1}{\epsilon(n)-\mu(n)}<\frac{2}{\epsilon(n)}$. The expected number of rewindings is bounded by $O(1/\widetilde{\epsilon})$ assuming $\widetilde{\epsilon}/\epsilon=O(1)$. By Markov's inequality, the probability that $\simu$ tries more than $n/\widetilde{\epsilon}$ iterations in any $n$ repetitions is at most $O(1/n)$. All repetitions fails with probability at most $O(1/n)^n$.
The case that $\widetilde{\epsilon}$ is not within a constant factor of $\epsilon(n)$ is negligible.
\end{enumerate}
\end{claim}

\begin{claim} The probability that $\simu$ outputs {\sf ambiguous} is negligible in $n$.
Intuitively, if there exists an infinite series of inputs for which $\simu$ outputs {\sf ambiguous} with non-negligible probability, then this can be used to break the computational binding of $\com_h$.
\end{claim}

\begin{algorithm}
\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
$\simu^{V^*(x,z,r,\cdot)}(G;r)$\;
\Input{$G=(V,E)$, with $V=\{v_1,\ldots,v_n\}$}
\Output{A simulated view close to real view of $V^*$.}
``Send'' $V^*$ the first message of $\com_h$\;
``Receive'' from $V^*$ an commitment $c$ to some query string $q=(e_1,\ldots,e_N),N=n\cdot\abs{E}$ and receive back its reply\;
``Send'' $V^*$ $N$ vectors of $n$ commitments to $0$\;
\If{$V^*$ {\bf aborts} or $\decom_h(c)$ is invalid}{
    {\bf Output} $\perp$
}\Else{
    
    Let $q=(e_1,\ldots,e_N)$ be the decommitted value.\;
    $m\gets 0$\;
    $ctr\gets 0$\;
    \While{$m<12n$}{
    	$ctr\gets ctr+1$
    	execute {\bf Step 4}\;
	\If{$\decom_h(c)$ is valid}{
		$m\gets m+1$\;
	}
    }
    $\widetilde{\epsilon}\gets \frac{m}{ctr}$\;
    \For{$i=1,\ldots,n$}{
    \For{$j=1,\ldots ,n / \widetilde{\epsilon} $} {
    Generate $N$ vectors of commitments $\vec{c_1},\ldots,\vec{c_N}$ as original protocol.\;
    	\If{$V^*$ provides a valid decommitment to $q$}{
		{\bf break}\;
    	}
	\If{$V^*$ provides a valid decommitment to $q'\neq q$}{
		{\bf output} {\sf ambiguous}\; {\bf halts}\;
	}
	\If{the total running time $> 2^{-n}$}{{\bf output} {\sf fails}\;}
    }}
    Completes the proof by handing $V^*$ decommitments.
}

\caption{Simulator of Protocol~\ref{proto:zk-3-color-constant}.}\label{alg:zk-3-color-constant-sim}
\end{algorithm}

\end{proof}